\propertitle

### 2020-03-16 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T22:12:34+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

As stated on p.~8, the interpretation is important because it leads to
numerically different results in first- and higher-order approximations.
And such approximations may be necessary in the precise calculation of the
evidence, as explained in the reply to the previous point. Appendix~C
explains where and why the numerical differences appear. Also, it is
important to know whether we are calculating the frequency of past results,
or the probability for a new result, or the most probable frequency of
future results. These three quantities can be numerically very different
when the ratio $\frac{\text{\# samples}}{\text{data-space dimension}}$ is
high, and they are to be used in different ways.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T00:35:35+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

As stated on p.~8, the interpretation is important because it leads to
numerically different results in first- and higher-order approximations.
And such approximations may be necessary in the precise calculation of the
evidence, as explained in the reply to the previous point. Appendix~C
explains where and why the numerical differences appear. Also, it is
important to know whether we are calculating the frequency of past results,
or the probability for a new result, or the most probable frequency of
future results. These three quantities can be numerically very different
when the ratio $\frac{\text{\# samples}}{\text{data-space dimension}}$ is
high, and they are to be used in different ways. Preliminary calculations
from the full Bayesian analysis show that%
\setlength{\intextsep}{-1ex}% with wrapfigure
\setlength{\columnsep}{0ex}% with wrapfigure
\begin{wrapfigure}{r}{0pt} % with wrapfigure
\centering\includegraphics[width=0.5\linewidth]{example_fullbayesian.pdf}
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% exp_family_maxent.nb
the most probable frequency distribution across recorded bins (item i on
p.~8) and the belief distribution over the total activity at any recorded
bin (item ii on p.~8) are visibly different. See figure on the right: the
first is the red dashed red curve, the second the solid green line.
